Consumer extinctions constrain phenotypic evolution in the resulting food web

### 2019-08-30 analyses/reproduce_analyses.Rmd
add calculations of curvature differences between treatments as well as effects on evolvability.

```{r required libraries, results='hide'}
# Load required libraries.
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption
```

@@

```{r Curvature, include=FALSE}
# Calculate curvatures for original food web
foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)

# Calculate curvatures for extinction food web
foodweb_extinction_raw_curvs <- foodweb_extinction_raw_gradients %>%
  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)

@@

@@

>>>>

```{r required libraries, results='hide'}
# Load required libraries.
library(evolqg)     # calculate evolvability
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption
```

@@

```{r Curvature, include=FALSE}
# Get mean estimates for directional selection gradients
foodweb_original_mean_sc.Diam <- filter(tidy_foodweb_grads, type == "Original", term == "sc.Diam")$mean
foodweb_original_mean_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Original", term == "sc.log.Clutch")$mean
foodweb_original_mean_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Original", term == "sc.sqrt.Pref")$mean

foodweb_extinction_mean_sc.Diam <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.Diam")$mean
foodweb_extinction_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.log.Clutch")$mean
foodweb_extinction_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean

# Calculate curvatures for original food web
foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.Diam, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - foodweb_original_mean_sc.sqrt.Pref*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.sqrt.Pref, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_extinction_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)

# Calculate curvatures for extinction food web
foodweb_extinction_raw_curvs <- foodweb_extinction_raw_gradients %>%
  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_mean_sc.Diam, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - foodweb_extinction_sc.log.Clutch*foodweb_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - foodweb_extinction_sc.sqrt.Pref*foodweb_extinction_sc.sqrt.Pref,# `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_sc.sqrt.Pref,# `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - foodweb_extinction_sc.log.Clutch*foodweb_extinction_sc.sqrt.Pref)# `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)

@@

## Long-term selection gradients for the gall midge: food-web treatments

```{r Long-term food-web selection gradients, echo=TRUE}

# Nothing changes for the original food web

# use mean fitness from original food-web treatment to approximate long-term fitness of Extinction food web
# once egg parasitoids increase in abundance after being released from intraguild predation
foodweb_long_extinction_gradient <- function(x) foodweb_extinction_mean_brackets * x / foodweb_original_mean_fitness

foodweb_long_extinction_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebExtinction:")) %>%
  transmute_all(funs(foodweb_long_extinction_gradient))
```

```{r Tidy up long-term selection gradients}
# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_long_grads <- bind_cols(foodweb_original_raw_gradients, foodweb_long_extinction_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_long_grads <- foodweb_long_grads %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

We then calculate selection gradients and 95% confidence intervals.

```{r Table of long-term food web selection gradients}
tidy_foodweb_long_grads %>%
  filter(type != "Diff") %>%
  #select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
  arrange(desc(Term)) %>%
  knitr::kable(., caption = "Table of long-term standardized selection gradients acting on gall midges in each food-web treatment.")
```

```{r Table of differences in long-term selection gradients between food-web treatments}
tidy_foodweb_long_grads %>%
  filter(type == "Diff") %>%
  #select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of differences in long-term selection gradients acting on gall traits between food-web treatment.")
```

```{r Curvature long-term, include=FALSE}
# Get mean estimates for directional selection gradients
# Note we already have the mean estimates for the original food web

foodweb_long_extinction_mean_sc.Diam <- filter(tidy_foodweb_long_grads, type == "Extinction", term == "sc.Diam")$mean
foodweb_long_extinction_sc.log.Clutch <- filter(tidy_foodweb_long_grads, type == "Extinction", term == "sc.log.Clutch")$mean
foodweb_long_extinction_sc.sqrt.Pref <- filter(tidy_foodweb_long_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean

# Calculate curvatures for original food web
foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.Diam, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.log.Clutch, #`FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - foodweb_original_mean_sc.sqrt.Pref*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.log.Clutch, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.sqrt.Pref)# `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)

# Calculate long-term curvatures for extinction food web
foodweb_long_extinction_raw_curvs <- foodweb_long_extinction_raw_gradients %>%
  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - foodweb_long_extinction_mean_sc.Diam*foodweb_long_extinction_mean_sc.Diam, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - foodweb_long_extinction_sc.log.Clutch*foodweb_long_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - foodweb_long_extinction_sc.sqrt.Pref*foodweb_long_extinction_sc.sqrt.Pref, # `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - foodweb_long_extinction_mean_sc.Diam*foodweb_long_extinction_sc.log.Clutch, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - foodweb_long_extinction_mean_sc.Diam*foodweb_long_extinction_sc.sqrt.Pref, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - foodweb_long_extinction_sc.log.Clutch*foodweb_long_extinction_sc.sqrt.Pref) # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_long_curvs <- bind_cols(foodweb_original_raw_curvs, foodweb_long_extinction_raw_curvs) %>%
  mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
         `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
         `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
         `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
         `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
         `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_long_curvs <- foodweb_long_curvs %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"))#,
         #gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
         #                       ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         #mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         #conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         #conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

```{r Table of long-term food web curvatures}
tidy_foodweb_long_curvs %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of long-term curvatures on gall traits in each food-web treatment.")
```

```{r Table of differences in long-term curvatures between food-web treatments, include=FALSE}
tidy_foodweb_long_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of differences in long-term curvatures on gall traits between food-web treatment.")
```

```{r Plot long-term food-web gradients, fig.cap="Plot of long-term standardized selection gradients acting on gall midges in each food-web treatment."}

# Plot helpers
dodge_width <- position_dodge(width=0.5)
y_limits_foodweb_long_grads <- c(min(filter(tidy_foodweb_long_grads, type!="Diff")$conf.low), 
                            max(filter(tidy_foodweb_long_grads, type!="Diff")$conf.high))
P_asterisk_foodweb_grads <- 0.5
P_size <- 8
legend_foodweb_long_labels <- c("Original","Extinction-Long")
legend_foodweb_title <- "Food web"
point.size <- 3

# Plot directional selection gradients
plot_foodweb_long_directional_grads <- tidy_foodweb_long_grads %>%
  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_long_grads) +
  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
  facet_wrap(~gradient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title)

# Plot quadratic selection gradients
plot_foodweb_long_quadratic_grads <- tidy_foodweb_long_grads %>%
  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_long_grads) +
  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
  facet_wrap(~gradient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title)

# Plot correlational selection gradients
plot_foodweb_long_correlational_grads <- tidy_foodweb_long_grads %>%
  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_long_grads) +
  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
  facet_wrap(~gradient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title)

# Get legend
legend_foodweb_long_grads <- get_legend(plot_foodweb_long_directional_grads)

# Format plots for manuscript
plot_foodweb_long_grads <- plot_grid(
  plot_foodweb_long_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
  plot_foodweb_long_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
  plot_foodweb_long_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
  nrow=2, align="hv", labels = "")
plot_legend_foodweb_long_grads <- ggdraw(plot_foodweb_long_grads) + draw_grob(legend_foodweb_long_grads, x = 0.7, y=-0.2)
y_title_foodweb_long_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)

figure_foodweb_long_grads <- plot_grid(y_title_foodweb_long_grads, plot_legend_foodweb_long_grads, ncol=2, rel_widths = c(0.05,1)) 
figure_foodweb_long_grads
```

@@

```{r Genetic constraints, include=F, eval=F}
bootstrapped_foodweb_curvs <- bind_cols(foodweb_original_raw_curvs, foodweb_extinction_raw_curvs) #%>%
  #mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
  #       `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
  #       `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
  #       `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
  #       `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
  #       `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`)
#bootstrapped_foodweb_curvs

Pmat <- matrix(diag(c(1,1,1)), byrow = T, ncol = 3)#cov(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref))
Gmat <- 0.3*Pmat # assuming heritability of 0.3

registerDoParallel(cores = 32)
foodweb_original_genetic_constraints <- c()
foodweb_extinction_genetic_constraints <- c()
for(i in 1:dim(bootstrapped_foodweb_curvs)[1]){ #

  # original
  original_C <- matrix(c(bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],
                    bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],
                    bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Pref`[i]),
                  byrow = T, ncol = 3)
  original_new_G <- Gmat + Gmat %*% original_C %*% Gmat
  original_new_G2 <- original_new_G + original_new_G %*% original_C %*% original_new_G
  original_new_G3 <- original_new_G2 + original_new_G2 %*% original_C %*% original_new_G2
  original_new_G4 <- original_new_G3 + original_new_G3 %*% original_C %*% original_new_G3
  original_new_G5 <- original_new_G4 + original_new_G4 %*% original_C %*% original_new_G4
  original_new_G6 <- original_new_G5 + original_new_G5 %*% original_C %*% original_new_G5
  original_new_G7 <- original_new_G6 + original_new_G6 %*% original_C %*% original_new_G6
  original_new_G8 <- original_new_G7 + original_new_G7 %*% original_C %*% original_new_G7

  foodweb_original_genetic_constraints[i] <- try(MeanMatrixStatistics(original_new_G, iterations = 1000, parallel = TRUE))["evolvability"]

  # extinction
  extinction_C <- matrix(c(bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Pref`[i],
                    bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],
                    bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Pref`[i]),
                  byrow = T, ncol = 3)
  extinction_new_G <- Gmat + Gmat %*% extinction_C %*% Gmat
  extinction_new_G2 <- extinction_new_G + extinction_new_G %*% extinction_C %*% extinction_new_G
  extinction_new_G3 <- extinction_new_G2 + extinction_new_G2 %*% extinction_C %*% extinction_new_G2
  extinction_new_G4 <- extinction_new_G3 + extinction_new_G3 %*% extinction_C %*% extinction_new_G3
  extinction_new_G5 <- extinction_new_G4 + extinction_new_G4 %*% extinction_C %*% extinction_new_G4
  extinction_new_G6 <- extinction_new_G5 + extinction_new_G5 %*% extinction_C %*% extinction_new_G5
  extinction_new_G7 <- extinction_new_G6 + extinction_new_G6 %*% extinction_C %*% extinction_new_G6
  extinction_new_G8 <- extinction_new_G7 + extinction_new_G7 %*% extinction_C %*% extinction_new_G7

  foodweb_extinction_genetic_constraints[i] <- try(MeanMatrixStatistics(extinction_new_G, iterations = 1000, parallel = TRUE))["evolvability"]

  # progress
  print(paste(i/dim(bootstrapped_foodweb_curvs)[1]*100, "% done!"))
}

## Note that higher values of conditional evolvability indicate less genetic constraints

# heritability does affect constraints

bootstrapped_genetic_constraints <- data.frame(Original = as.numeric(foodweb_original_genetic_constraints), Extinction = as.numeric(foodweb_extinction_genetic_constraints)) %>%
  mutate(Diff = Original - Extinction)

bootstrapped_summary_constraints <- bootstrapped_genetic_constraints %>%
summarise_all(list(~mean(., na.rm = T), ~quantile(., probs=0.975, na.rm = T), ~quantile(., probs=0.025, na.rm = T))) %>%
  gather(key = type, value = Estimate) %>%
  separate(col = type, into = c("Foodweb", "Type")) %>%
  arrange(Foodweb)

sum(bootstrapped_genetic_constraints$Diff > 0) / length(bootstrapped_genetic_constraints$Diff)

bootstrapped_summary_constraints

bootstrapped_genetic_constraints %>%
  ggplot(., aes(x = Diff)) +
  geom_histogram() +
  geom_vline(xintercept = 0, linetype = "dotted")
```

```{r mean curvature effects on random G-matrices}
# Generate random G-matrices
random_Gmats <- RandomMatrix(num.traits = 3, num.matrices = 10000, min.var = 0, max.var = 0.5)

## Get mean estimates for curvature matrix

# Original
foodweb_original_mean_C.Diam <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Diam")$mean
foodweb_original_mean_C.Clutch <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Clutch")$mean
foodweb_original_mean_C.Pref <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Pref")$mean
foodweb_original_mean_C.Diam.Clutch <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Diam:Clutch")$mean
foodweb_original_mean_C.Diam.Pref <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Diam:Pref")$mean
foodweb_original_mean_C.Clutch.Pref <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Clutch:Pref")$mean
